%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
% BK said : Thx you Aras Gungore!
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Handsome(?) Sheen} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:88609xxxxxxxx}{+886 9xx xxx xxx}
    $|$
    \faAt \hspace{.5pt} \href{mailto:abc123@gmail.com}{abc123@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/yourname/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/yourname}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://www.cake.me/yourname}{Visual CV}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/%E5%9C%8B%E7%AB%8B%E4%B8%AD%E8%88%88%E5%A4%A7%E5%AD%B8/@24.1235569,120.6727457,17z/data=!3m1!4b1!4m6!3m5!1s0x34693cfcecffe9d9:0xe28afadc0dad203a!8m2!3d24.123552!4d120.675326!16zL20vMDR4cDF6?authuser=0&entry=ttu&g_ep=EgoyMDI1MTAyOS4yIKXMDSoASAFQAw%3D%3D
\end{center}

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
   \resumeEducationHeading
      {National Chung Hsing University
      }{Taichung, Taiwan}
      {M.S. in Information Management;   \textbf{GPA: 3.78/4.30}}{Sep 2021 \textbf{--} Jun 2024}
      {Information Security and Blockchain Applications Lab{}}{}
    \resumeEducationHeading
      {National Formosa University
      }{Yunlin, Taiwan}
      {B.S. in Information Management;   %\textbf{GPA: 2.9/4.30}
      } {Sep 2016 \textbf{--} Jun 2020}{}{}
      
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
         \textbf{Programming Languages:} Python, Java, JavaScript, C++, C\#, MATLAB, Scala, PHP \\[3pt]
        \textbf{Web \& Database Technologies:} HTML, CSS, Flask, Django, Firebase, MongoDB, MySQL, SQL \\[3pt]
        \textbf{Frameworks \& Tools:} TensorFlow, Keras, PyTorch, Scikit-learn, OpenCV, Docker, VMware, Kali Linux \\[3pt]
        \textbf{Blockchain / DLT:} Hyperledger Fabric, Solidity
        
     }}
  \resumeSubHeadingListEnd

%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {National Chung Hsing University (NCHU)}{Taichung, Taiwan}
      {Research Assistant}{Sep 2021 \textbf{--} May 2024}
        \resumeItemListStart
            \resumeItem{Engineered a digital warranty management system to replace paper workflows using Flask and MongoDB, improving scalability and data integrity.}
            \resumeItem{Integrated Hyperledger to establish a private blockchain on Ubuntu, enabling secure and verifiable data transactions.}
            \resumeItem{Developed a real-time feedback analysis platform using Firebase and Flask for student response visualization.}
            \resumeItem{Applied machine learning within the STEAM framework to analyze instructional data, resulting in three international conference papers.}
            \resumeItem{Developed interactive \textbf{VR-based educational modules} in Unity to enhance classroom engagement and experiential learning.}
            \resumeItem{Designed and implemented \textbf{cybersecurity lab exercises} (e.g., Nmap, SQLMap, Wireshark) to provide hands-on training in network analysis and ethical hacking.}
        \resumeItemListEnd

    \resumeSubheading
      {Science and Technology Policy Research and Information Center, NARLabs}{Tainan, Taiwan}
      {Research Assistant}{Jul 2022 \textbf{--} Jun 2023}
        \resumeItemListStart
            \resumeItem{Conducted Deepfake detection research at the Cybersecurity Center of Excellence (CCoE), funded by the \href{https://www.stpi.niar.org.tw/}{\color{blue}National Science and Technology Council (NSTC)}, Taiwan.}
            \resumeItem{Designed and deployed the \textbf{TWHD (Taiwan High-quality Deepfake Dataset)} to improve detection accuracy for Taiwanese facial data, benchmarking it against KoDF, FaceForensics++, and DFDC datasets.}
            \resumeItem{Implemented and optimized Deepfake detection pipelines using \textbf{ResNet}, \textbf{Transformer}, and \textbf{XceptionNet} architectures in \textbf{TensorFlow} and \textbf{PyTorch}.}
            \resumeItem{Contributed to a team project developing a web-based Deepfake detection platform by refining data preprocessing workflows and improving dataset quality to enhance model accuracy.}
        \resumeItemListEnd
        %\newpage

    \resumeSubheading
      {National Chung Hsing University (NCHU)}{Taichung, Taiwan}
      {Teaching Assistant}{Sep 2022 \textbf{--} Jun 2023}
        \resumeItemListStart
            \resumeItem{Assisted in teaching \textit{Programming and Application} and \textit{App Mobile Devices} courses for non-technical students.}
            \resumeItem{Demonstrated strong Python proficiency by designing lab exercises, guiding debugging sessions, and explaining core programming logic in beginner-friendly terms.}
        \resumeItemListEnd
    
    \resumeSubHeadingListEnd
    
    %\newpage
    
%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
    {\textbf{MailGuard} — Local LLM-Based Email Security Automation}{}
    \resumeItemListStart
      \resumeItem{Developed a local AI-driven email security pipeline using \textbf{Ollama (Llama model)} integrated with \textbf{n8n}, enabling secure \textbf{on-device inference} for automated email analysis and response.}
      \resumeItem{Implemented a dual-layer LLM system where the local model detects and sanitizes potential security threats such as \textbf{prompt injection}, encoded payloads, and embedded commands before forwarding to \textbf{Gemini} for automatic reply generation.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Trusted Data Marketplace Based on IOTA Blockchain}}{}
        \resumeItemListStart
          \resumeItem{Built a membership management platform integrating product warranty information, leveraging \textbf{IOTA blockchain} to ensure data immutability and traceability.}
          \resumeItem{Tech Stack: \textbf{Flask, Nginx, MongoDB, Hyperledger, HTML/CSS/JavaScript}}
        \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{Educational Management Platform Development}}{}
        \resumeItemListStart
          \resumeItem{Developed a course management system integrating student grades, records, and survey data into a \textbf{Flask–Firebase} backend with a searchable analytics dashboard.}
        \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{Stock Price Prediction Using Deep Learning and Regression Models}}{}
        \resumeItemListStart
          \resumeItem{Implemented stock trend forecasting using \textbf{TensorFlow} and \textbf{Keras}-based LSTM architectures, fine-tuning hyperparameters (learning rate, batch size, sequence length) to optimize model performance.}
          \resumeItem{Compared model results across regression techniques (Linear, Lasso, Ridge, Polynomial, Decision Tree, Logistic Regression) using accuracy, F1-score, and loss metrics.}
          \resumeItem{Enhanced overall model precision through systematic data preprocessing and feature engineering.}
        \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{Smart Contract Development and Deployment}}{}
        \resumeItemListStart
          \resumeItem{Developed and deployed \textbf{Solidity} smart contracts using \textbf{Remix IDE} and \textbf{MetaMask}, implementing transaction logging, role-based access control, and automated fund transfers.}
        \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{VR Educational Game Development and Design}}{}
        \resumeItemListStart
          \resumeItem{Designed and developed an immersive VR educational game using \textbf{Unity}, combining interactive gameplay with instructional content to enhance learning engagement.}
          \resumeItem{Planned gameplay flow and learning objectives, conducted iterative testing and optimization for system stability and learning outcomes.}
        \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{Smart Tourism and Air Quality Information Platform}}{}
        \resumeItemListStart
          \resumeItem{Developed a responsive web platform combining tourism information with real-time weather and air quality data using open APIs from Taiwan’s Environmental Protection Administration.}
          \resumeItem{Implemented web crawling and data visualization to integrate travel blog content and enhance user experience and decision-making.}
        \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{Amazon KDD Cup 2022}}{}
        \resumeItemListStart
          \resumeItem{Participated in the global \textbf{Amazon KDD Cup 2022} competition as a team member, using a \textbf{BERT-based model} to predict product similarity and achieved benchmark-level performance.}
          \resumeItem{Gained experience in data preprocessing, feature engineering, and model training for large-scale datasets.}
        \resumeItemListEnd
    
    \resumeProjectHeading
        {\textbf{AI-Based Fish Species Recognition System Platform}}{}
        \resumeItemListStart
          \resumeItem{Developed a deep learning-based fish species recognition platform using \textbf{PyTorch (YOLOv5)}, trained on custom datasets with tuned confidence thresholds and non-max suppression parameters for improved detection accuracy.}
          \resumeItem{The project passed the first-stage review and was invited for an on-site presentation to industry evaluators.}
        \resumeItemListEnd

      
    \resumeSubHeadingListEnd

%----------- Publications & Research Outputs -----------

\newenvironment{publist}{
  \begin{itemize}[leftmargin=0em, itemsep=4pt, label={}]
}{
  \end{itemize}
}

\section{Publications \& Research Outputs}
\vspace{4pt}
\begin{publist}
    \item \textbf{TWHD: Taiwan Pioneering Deepfake Dataset for Multi-Face Forgery Detection}, Master’s Thesis, National Chung Hsing University (NCHU), 2024.
    \item \textbf{Enhancement of Information Security Literacy of University Students in Programming Courses}, \textit{ASET 2022 – 38th Science Education Conference}.
    \item \textbf{Using Flowcharting as a Modeling Tool in Programming STEAM Learning}, \textit{ASET 2022 – 38th Science Education Conference}.
    \item \textbf{Undergraduate Students’ Technological Cognition and Risk Perception on Information Ethics}, \textit{ISTEM-ED 2024 – Singapore International STEM Education Conference}.
\end{publist}

\end{document}
